\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 lang-design.tex
Save comments from discussion.

\subsection{Design Space}

>>>>

\subsection{Design Space}\YZ{I was thinking if the paper should start by talking about the functional encoding of inheritance (namely exposing a self parameter to allow late binding, and later taking the fixpoint of the extensible module when it needs to be accessed outside the family).  I think most readers will benefit from a recap of this encoding.\\
Coq is total but that doesn’t prevent Coq from having a Fixpoint keyword (plus you proved your language is consistent).
}
